\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-03-20 paper/main.tex
Tool availability placeholder
Added stats about bug type

@@

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build, and column ``environment'' shows the breakdown
of instances for each kind of environment to reproduce the bug.

@@

>>>>

\Fix{Add a "Tool availablity" section and move the details there, upload the video to YouTube, archive 
the tool at zenodo}

@@

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build, and column ``environment'' shows the breakdown
of instances for each kind of environment to reproduce the bug. Co-incidentally,
all bugs that require a GPU build are reproduced using a docker
container i.e. the column venv-docker is the same as bugs reproducible with CPU-GPU builds
of the libraries respectively. Table~\ref{table:bug-stats} shows whay type of error is manifested
due to each bug instance. In total, we have 15 different types of bug manifestations across
the three libraries.

\Fix{Added table and description, please revise}

@@

\begin{table}
  \centering
  \caption{\label{table:bug-stats}Different bug manifestation types from \tname.}
  \begin{tabular}{lrrrr}\toprule
    Bug manifestation type &Jax &Pytorch &Tensorflow \\\midrule
    Internal Exception &11 &9 &1 \\
    Incorrect Output &14 &11 &5 \\
    Value Error &7 &0 &3 \\
    Type Error &3 &2 &3 \\
    Attribute Error &2 &0 &0 \\
    Index Error &2 &1 &0 \\
    Floating Point Error &1 &0 &0 \\
    Error Not Raised &1 &0 &0 \\
    Parse Error &1 &0 &0 \\
    Runtime Error &1 &7 &1 \\
    Not Implemented Error &1 &0 &0 \\
    Memory Error &1 &1 &0 \\
    Invalid Argument Error &1 &0 &1 \\
    Crash &0 &4 &10 \\
    Assertion Error &0 &2 &0 \\
    \midrule
    $\Sigma$ &46 &37 &24 \\
    \bottomrule
  \end{tabular}
\end{table}
